### 2019-10-16 README.Rmd
edits for paper content and tables for word
complete paper+analysis scaffold

## Objectives

## Design

## Setting

England and Wales.

## Outcome measures

## Results

@@

>>>>

## Background

The Enhanced Tuberculosis Surveillance (ETS) system is a routine surveillance system - with a similar structure to other such systems - that collects data on all notified tuberculosis (TB) cases in England. It is routinely used to study the epidemiology of TB. Routine data often has a large amount of missing data which may not be fully accounted for when used in analyses. This study explores the evidence for associations between missingness in several key outcomes and demographic variables. Any such associations may introduce bias if not accounted for.

## Methods

* Introduce ETS
* Data extraction and management
* Structure of the ETS
* Data completeness
* Drivers of variable completeness (regression)

## Results *Copy from bottom*

* Missing structure
* Drivers of variable completeness

@@

* Surveillance data is likely to have a high degree of misising data. In the ETS missing for key outcomes is associated with demographic factors such as....
* To avoid biasing analysis studies should make use of imputed data - rather than complete case analysis - and extend their imputation models to other demographic variables that may not be included in the analysis model. 
* This analysis should be repeated in other datasets - for this reason the code is available as an R package.
